---
title: "Q Hacking -- Stats for Large Data Programming Challenge"
author: "Callithrix Jacchus"
date: "2023-09-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

In this document, we will outline our proposed solution for the Q Hacking Challenge as part of the Large Data Programming session. We will discuss the code and methods employed, concluding with a report of the results.

## Set Up Packages

```{r}
install.packages("ggplot2", repos = "http://cran.us.r-project.org")
install.packages("cowplot", repos = "http://cran.us.r-project.org")
install.packages("ggrepel", repos = "http://cran.us.r-project.org")
install.packages("htmlwidgets", repos = "http://cran.us.r-project.org")
install.packages("plotly", repos = "http://cran.us.r-project.org")
```

## Loading the Data

We need to load the required covid data. 
```{r}

library(dplyr)

data <- read.csv("https://covid.ourworldindata.org/data/owid-covid-data.csv", na.strings = "",header=T)
```

## Selecting a subset of data

As outlined in the guidelines, it's not necessary to conduct p-hacking on the entire dataset. Therefore, we opted to focus on a specific country for our analysis. In this example, we examine new COVID-19 cases in the United States across all available dates. To analyze data from a different country, one can simply modify the location parameter.

```{r}
data_country <- data[which(data$location=="United States"),] # One can modify the location parameter if they want to look into another country

data_newcases <- data_country %>% select("new_cases")

new_cases <- data_newcases$new_cases

vl <- length(new_cases)

print(paste("The length of the data selected is:", vl))
```


## Let's hack P Value

We opt to create a custom variable by populating the time series with random values. We employ a 'while' loop to continuously regenerate these values until the p-value meets the significance threshold. 
```{r}
set.seed(123)

y <- new_cases 

p_value <- 1

while (p_value >= 0.05) {

  x <- cumsum(rnorm(vl))

  model <- lm(y ~ x)

  model_summary <- summary(model)

  p_value <- model_summary$coefficients[2, 4]

  print(paste("P is:", p_value))
}

# x should be a variable and y has a "significant" relationship with x
print("Done")
print(paste("The final P is:", p_value))
print(summary(model))
```
## Plotting 

```{r pressure}
library(ggplot2)

data_to_plot <- data.frame("Ours" = x, "Case" = y)

ggplot(data_to_plot, aes(x = Ours, y = Case)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_y_continuous(breaks = seq(min(data_to_plot$Case, na.rm = TRUE), max(data_to_plot$Case, na.rm = TRUE), by = 50000)) +
  ggtitle(paste("Significant Relationship between variable and New Cases, p =", p_value)) +
  xlab("Our Custom Variable") +
  ylab("New Cases")
```


